Standalone Tactics using OpenTheory

### 2012-02-13 paper.tex
ditch 1 reference for evidential tool bus

The idea of separate reasoning tools communicating to enhance a proof development environment is also being pursued in the Evidential Tool Bus~\cite{DBLP:conf/icfem/Rushby05,fk:etb} and the MathServe System~\cite{DBLP:conf/cade/ZimmerA06}.
This idea is a natural extension of the integration of automatic tools with interactive theorem provers.

>>>>

The idea of separate reasoning tools communicating to enhance a proof development environment is also being pursued in the Evidential Tool Bus~\cite{DBLP:conf/icfem/Rushby05} and the MathServe System~\cite{DBLP:conf/cade/ZimmerA06}.
This idea is a natural extension of the integration of automatic tools with interactive theorem provers.
